---
title: "Homework #1 -- Pet Names Dataset"
author: "Areeg"
date: "`r Sys.Date()`"
output: github_document
---

**Student ID:insert ID here**

**Deadline:** 23:59 on Saturday, 13 February 2021

**Total Points:** 30


## Loading Packages

```{r load-packages, message = FALSE}

library(tidyverse)
library(openintro)
library(ggrepel)
```


##Exercises

`1.

(4 points)


```{r}
```
Write your narrative here
52,519



`2.

(4 points)

```{r}

```
Write your narrative below

7

`3. Copy the code provided in the homework documentation and paste it here. 

(4 points)

```{r}
seattlepets %>%count(animal_name, sort = TRUE)
```
Write your narrative here

1.Lucy          
2.Charlie       
3.Luna 

`4.

(10 points)
```{r}
seattlepets %>%group_by(species) %>%count(animal_name, sort = TRUE)
seattlepets %>%count(species, sort = TRUE)

```


```{r species-name-top5, eval=TRUE}
 seattlepets %>%group_by(species) %>%count(animal_name, sort = TRUE)%>%slice_max(n, n = 5)%>%arrange(species, n)

```

`5.  What names are more common for cats than dogs? The ones above the line or the ones below the line?

Oliver  and  lily 
below the line

(4 points)

`6. Is the relationship between the two variables (proportion of cats with a given name and proportion of dogs with a given name) positive or negative? What does this mean in context of the data?

 Positive ,,  if dog names increase the cats names increase also and if dogs names Decrease the cats names Decrease also in the same name of them
 (4 points)